---
title: "Reproducible_Research"
author: "Six_Paths"
date: "12 octobre 2018"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

#### Reproductible Research ####

## === Week 1 === ##

# Loading and preprocessing the data

### 1. Get data 

```{r echo=TRUE}
  setwd("C:/Users/686004/Desktop/Six_Paths/D_S")
  library(data.table)
  download.file("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip", 
                destfile = "Week_2/Activity_Monitoring.zip", mode="wb")
  unzip(zipfile="Week_2/Activity_Monitoring.zip",exdir="Week_2")
  
  ## Loading the data
  data_AM <- data.table::fread("Week_2/activity.csv")
```

### 2. Process/transform the data into a format suitable for analysis

```{r echo=TRUE}
  ## Processing the data
  data_AM <- as.data.frame(data_AM)
  data_AM$date <- as.Date(as.character(data_AM$date), format ="%Y-%m-%d")
  head(data_AM)  
```


# Mean of total number of steps taken per day?

### 1. Histogram of the total number of steps taken each day

```{r, echo=TRUE}
  total_steps_days <- aggregate(steps~(as.Date(date)), 
                          data=data_AM, FUN=sum, na.rm=TRUE)
  hist(total_steps_days$steps, col = "darkmagenta",
       main = "Total number steps taken each day",
       xlab = "Steps per day")
  head(total_steps_days)
```

### 2. Mean and median steps taken each day

```{r, echo=TRUE}

  mean(total_steps_days$steps)
  median(total_steps_days$steps)

```

### 3. Time series plot of the average number of steps taken

```{r, echo=TRUE}

  average_steps_days <- aggregate(steps~interval,
                                  data = data_AM, FUN = mean, na.rm=TRUE)
  plot(average_steps_days, type="l", col  ="darkgreen",
       main = "Average steps taken in 5-minute interval",
       xlab = "5-minutes interval", ylab = "Steps average")
  head(average_steps_days)
```

# Daily activity pattern's average

### 1. The 5-minute interval, on average across all the days, contains the maximum number of steps?

```{r, echo=TRUE}

  average_steps_days[which.max(average_steps_days$steps), 1]

```

### 2.  Total number of missing values in the dataset 

```{r, echo=TRUE}

  sum(is.na(data_AM))

```

# Imputing missing values

### 1. New dataframe with filling missing data

```{r, echo=TRUE}
  
  data_AM_fillNA <- data_AM
  data_AM_fillNA[is.na(data_AM_fillNA$steps), 1] <- mean(data_AM$steps, 
                                                         na.rm = TRUE)
  
```

### 2. Histogram of the total number of steps taken each day
  
```{r, echo=TRUE}
  
  total_steps_days_fillNA <- aggregate(steps~(as.Date(date)), 
                                data=data_AM_fillNA, FUN=sum, na.rm=TRUE)
  hist(total_steps_days_fillNA$steps, col = "darkmagenta",
       main = "Total number steps taken each day",
       xlab = "Steps per day")
  
```

### 3. Mean and median steps taken each day
 
```{r, echo=TRUE}

  mean(total_steps_days_fillNA$steps)
  median(total_steps_days_fillNA$steps)
  
```

### 4. Create factor variable with two levels : "weekday" or "weekend" 

```{r, echo=TRUE}
    
  data_AM_fillNA$week_day_end <- ifelse ((weekdays(as.Date(data_AM_fillNA$date)) %in% c('samedi', 'dimanche')),"weekend", "weekday")
  head(data_AM_fillNA)
  
```

# Check differences in activity patterns between weekdays and weekends

### 1. New factor variable in the dataset with two levels - "weekday" and "weekend" indicating whether a given date is a weekday or weekend day

```{r, echo=TRUE}
  
  average_steps_days_week <- aggregate(steps~ interval + week_day_end, 
                                       data=data_AM_fillNA, FUN=mean,
                                       na.rm=TRUE)
  head(average_steps_days_week)
```

### 2. Panel time series plot of the 5-minute interval (average) number of steps taken, averaged across all weekday days or weekend days. 

```{r, echo=TRUE}

  library(lattice)
  xyplot(steps ~ interval | week_day_end, average_steps_days_week, 
         type="l", lwd=1, layout=c(1,2),
         xlab="Interval", ylab="Number of steps")
  
```

  
